Details of specific functions

### 2020-09-04 inst/gitbook/03_specific-tutorials.Rmd
Added manuals for group.dist

Level | Name | Description | Source | 
------|------|---------------------------------------------------|--------|
2 | `ancestral.dist` | The distance between an element and its ancestor | `dispRity` |
2 | `angles` | The angle of main variation of each dimensions | `dispRity` |
2 | `centroids`<sup>1</sup> | The distance between each element and the centroid of the ordinated space | `dispRity` |
1 | `convhull.surface` | The surface of the convex hull formed by all the elements | [`geometry`](https://cran.r-project.org/web/packages/geometry/index.html)`::convhulln$area` |
1 | `convhull.volume` | The volume of the convex hull formed by all the elements | [`geometry`](https://cran.r-project.org/web/packages/geometry/index.html)`::convhulln$vol` |
2 | `deviations` | The minimal distance between each element and a hyperplane | `dispRity` |
1 | `diagonal` | The longest distance in the ordinated space (like the diagonal in two dimensions) | `dispRity` |
2 | `displacements` | The ratio between the distance from a reference and the distance from the centroid | `dispRity` |
1 | `ellipse.volume`<sup>1</sup> | The volume of the ellipsoid of the space | Donohue _et al._ (2013) |
1 | `func.div` | The functional divergence (the ratio of deviation from the centroid) | `dispRity` (similar to [`FD`](https://cran.r-project.org/web/packages/FD/index.html)`::dbFD$FDiv` but without abundance)|
1 | `func.eve` | The functional evenness (the minimal spanning tree distances evenness) | `dispRity` (similar to [`FD`](https://cran.r-project.org/web/packages/FD/index.html)`::dbFD$FEve` but without abundance)|
1 | `mode.val` | The modal value | `dispRity` |
1 | `n.ball.volume` | The hyper-spherical (*n*-ball) volume | `dispRity` |
2 | `neighbours` | The distance to specific neighbours (e.g. the nearest neighbours - by default) | `dispRity` |
2 | `pairwise.dist` | The pairwise distances between elements | [`vegan`](https://cran.r-project.org/web/packages/vegan/index.html)`::vegist` |
2 | `quantiles` | The *n*th quantile range per axis | `dispRity` |
2 | `radius` | The radius of each dimensions | `dispRity` |
2 | `ranges` | The range of each dimension | `dispRity` |
2 | `span.tree.length` | The minimal spanning tree length | [`ape`](https://cran.r-project.org/web/packages/vegan/index.html) (but see also [`vegan`](https://cran.r-project.org/web/packages/vegan/index.html)`::spantree`) |
2 | `variances` | The variance of each dimension | `dispRity` |

@@

>>>>

Level | Name | Description | Source | 
------|------|---------------------------------------------------|--------|
2 | `ancestral.dist` | The distance between an element and its ancestor | `dispRity` |
2 | `angles` | The angle of main variation of each dimensions | `dispRity` |
2 | `centroids`<sup>1</sup> | The distance between each element and the centroid of the ordinated space | `dispRity` |
1 | `convhull.surface` | The surface of the convex hull formed by all the elements | [`geometry`](https://cran.r-project.org/web/packages/geometry/index.html)`::convhulln$area` |
1 | `convhull.volume` | The volume of the convex hull formed by all the elements | [`geometry`](https://cran.r-project.org/web/packages/geometry/index.html)`::convhulln$vol` |
2 | `deviations` | The minimal distance between each element and a hyperplane | `dispRity` |
1 | `diagonal` | The longest distance in the ordinated space (like the diagonal in two dimensions) | `dispRity` |
2 | `displacements` | The ratio between the distance from a reference and the distance from the centroid | `dispRity` |
1 | `ellipse.volume`<sup>1</sup> | The volume of the ellipsoid of the space | Donohue _et al._ (2013) |
1 | `func.div` | The functional divergence (the ratio of deviation from the centroid) | `dispRity` (similar to [`FD`](https://cran.r-project.org/web/packages/FD/index.html)`::dbFD$FDiv` but without abundance)|
1 | `func.eve` | The functional evenness (the minimal spanning tree distances evenness) | `dispRity` (similar to [`FD`](https://cran.r-project.org/web/packages/FD/index.html)`::dbFD$FEve` but without abundance)|
1 | `group.dist` | The distance between two groups | `dispRity` |
1 | `mode.val` | The modal value | `dispRity` |
1 | `n.ball.volume` | The hyper-spherical (*n*-ball) volume | `dispRity` |
2 | `neighbours` | The distance to specific neighbours (e.g. the nearest neighbours - by default) | `dispRity` |
2 | `pairwise.dist` | The pairwise distances between elements | [`vegan`](https://cran.r-project.org/web/packages/vegan/index.html)`::vegist` |
2 | `quantiles` | The *n*th quantile range per axis | `dispRity` |
2 | `radius` | The radius of each dimensions | `dispRity` |
2 | `ranges` | The range of each dimension | `dispRity` |
2 | `span.tree.length` | The minimal spanning tree length | [`ape`](https://cran.r-project.org/web/packages/vegan/index.html) (but see also [`vegan`](https://cran.r-project.org/web/packages/vegan/index.html)`::spantree`) |
2 | `variances` | The variance of each dimension | `dispRity` |

@@

#### Between group metrics

The `group.dist` metric allows to measure the distance between two groups in the multidimensional space.
This function needs to intake several groups and use the option `between.groups = TRUE` in the `dispRity` function.
It calculates the vector normal distance (euclidean) between two groups and returns 0 if that distance is negative.
Note that it is possible to set up which quantiles to consider for calculating the distances between groups.
For example, one might be interested in only considering the 95% CI for each group.
This can be done through the option `probs = c(0.025, 0.975)` that is passed to the `quantile` function.
It is also possible to use this function to measure the distance between the groups centroids by calculating the 50% quantile (`probs = c(0.5)`).

```{r}
## Creating a dispRity object with two groups
grouped_space <- custom.subsets(dummy_space,
                      group = list(c(1:5), c(6:10)))

## Measuring the minimum distance between both groups
summary(dispRity(grouped_space, metric = group.dist,
                 between.groups = TRUE))

## Measuring the centroid distance between both groups
summary(dispRity(grouped_space, metric = group.dist,
                 between.groups = TRUE, probs = 0.5))

## Measuring the distance between both group's 75% CI
summary(dispRity(grouped_space, metric = group.dist,
                 between.groups = TRUE, probs = c(0.25, 0.75)))
```
